Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2021-01-15 paper.tex
Update on Overleaf.

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
%%%%%%
% Notes: 
% plot grouping/hue +
% table smallcaps +
% Time score memory center +
% Abstract
% Differences between infuser and us+
% time skecth diff between us +
% neden 0.005 +
% active vertex colors +

@@

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $\Gamma_G(v)$   & Neighborhood of incoming edges to vertex $v$ in graph $G$\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & Influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
\hline\hline
        %$p$             & Sampling probability for edges\\
%        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $X_{r..n}$      & Slice of Vector X between r and r+n(not including)\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $B$             & Batch size\\
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal Gain after last sketch build\\
        $\epsilon_{global}$    & Global estimation error threshold\\
        $\epsilon_{local}$    & Local estimation error threshold\\ 
        $\epsilon_{conv}$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

Since, $\epsilon_local$ is the maximum error allowed after the last rebuild. Setting $\epsilon_local$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results. Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked. But, the result quality will suffer. $\epsilon_global$, on the other hand, is the minimum influence we expected to obtain via building the sketch. If we were to set $\epsilon_global$ to 0, \acro will not rebuild the sketches, but when $\epsilon_global$ is set to infinity, we skill need to compare $\epsilon_local$ to estimation error before rebuilding.

@@

\begin{algorithm}
\caption{\sc{\acro}($G,K,J$)}
\label{algo:main}
\algorithmicrequire{$G = (V,E)$: the influence graph
\\\hspace*{6.6ex}{$K$: number of seed vertices
\\\hspace*{6.7ex}$\mathcal{J}$: number of MC simulations}\\}
\algorithmicensure{$S$: a seed set that maximizes influence on $G$
}
\begin{algorithmic}[1]
    \State {$S \leftarrow \{\emptyset\}$}
    \For{$ v\in V$} {\bf in parallel}
        \For{$ j\in J$}
            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
        \EndFor
    \EndFor
    \State $M \leftarrow simulate(G,M,\emptyset)$
    \State $mask \leftarrow zeros(J)$
    \State $\varsigma \leftarrow 0$
    \For{$k=1\ldots K$}
        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}} ~estimate(merge(mask,M_v))$
        \State $S \leftarrow S \cup \{s\}$
        \State $e \leftarrow estimate(merge(mask,M_s))$
        % \State $R_S \leftarrow run\_cascade(G,S,J)$
        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ }
        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
        \State $\delta = \sigma - \varsigma$
        \If{$ (e - \delta) / \delta < \epsilon_l \lor |e-\delta| / \sigma < \epsilon_g$}
            \State $mask \leftarrow merge(mask,M_s)$
        \Else
            \For{$ v\in V$} {\bf in parallel}
                \For{$ j\in J$}
                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
                \EndFor
            \EndFor
            \State $M \leftarrow simulate(G,M,R_S)$
            \State $mask \leftarrow zeros(J) $ 
            \State $\varsigma \leftarrow \sigma $ 
        \EndIf
    \EndFor
    \State \Return $S$
\end{algorithmic}
\end{algorithm}

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
%%%%%%
% add seconds to fig 7
% fix yaxis
% table 3-5 son satir 3-5
% fontlari buyult, relative score/time , fig 10 11
% notation
% Notes: 
% plot grouping/hue +
% table smallcaps +
% Time score memory center +
% Abstract
% Differences between infuser and us+
% time skecth diff between us +
% neden 0.005 +
% active vertex colors +

@@

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $\Gamma_G(v)$   & Neighborhood of incoming edges to vertex $v$ in graph $G$\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & Influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
\hline\hline
        %$p$             & Sampling probability for edges\\
%        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $X_{r..n}$      & Slice of Vector X between r and r+n(not including)\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $B$             & Batch size\\
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal Gain after last sketch build\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

Since, $\epsilon_{l}$ is the maximum error allowed after the last rebuild. Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results. Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked. But, the result quality will suffer. $\epsilon_{g}$, on the other hand, is the minimum influence we expected to obtain via building the sketch. If we were to set $\epsilon_{l}$ to 0, \acro will not rebuild the sketches, but when $\epsilon_{l}$ is set to infinity, we skill need to compare $\epsilon_{l}$ to estimation error before rebuilding.

@@

\begin{algorithm}
\caption{\sc{\acro}($G,K,J$)}
\label{algo:main}
\algorithmicrequire{$G = (V,E)$: the influence graph
\\\hspace*{6.6ex}{$K$: number of seed vertices
\\\hspace*{6.7ex}$\mathcal{J}$: number of MC simulations}\\}
\algorithmicensure{$S$: a seed set that maximizes influence on $G$
}
\begin{algorithmic}[1]
    \State {$S \leftarrow \{\emptyset\}$}
    \For{$ v\in V$} {\bf in parallel}
        \For{$ j\in J$}
            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
        \EndFor
    \EndFor
    \State $M \leftarrow simulate(G,M,\emptyset)$
    \State $mask \leftarrow zeros(J)$
    \State $\varsigma \leftarrow 0$
    \For{$k=1\ldots K$}
        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}} ~estimate(merge(mask,M_v))$
        \State $S \leftarrow S \cup \{s\}$
        \State $e \leftarrow estimate(merge(mask,M_s))$
        % \State $R_S \leftarrow run\_cascade(G,S,J)$
        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ }
        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
        \State $\delta = \sigma - \varsigma$
        \If{$ |(e - \delta) / \delta| < \epsilon_l \lor |e-\delta| / \sigma < \epsilon_g$} %FIXME
            \State $mask \leftarrow merge(mask,M_s)$
        \Else
            \For{$ v\in V$} {\bf in parallel}
                \For{$ j\in J$}
                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
                \EndFor
            \EndFor
            \State $M \leftarrow simulate(G,M,R_S)$
            \State $mask \leftarrow zeros(J) $ 
            \State $\varsigma \leftarrow \sigma $ 
        \EndIf
    \EndFor
    \State \Return $S$
\end{algorithmic}
\end{algorithm}
